---
title: "Lab03 - F tests for ANOVA"
output: pdf_document
---

## Goals

The goal in this lab is to practice F tests for ANOVA

## Loading packages

Here are some packages with functionality you may need for this lab.  Run this code chunk now.

```{r}
library(readr)
library(ggplot2)
library(gridExtra)
library(mosaic)
library(dplyr)

options("pillar.sigfig" = 10) # print 10 significant digits in summarize output
```

A study was conducted to examine the effectiveness of four different hand-washing methods for eliminating bacteria

```{r}
soap <- read_csv("http://www.evanlray.com/data/sdm4/Bacterial_Soap.csv")
names(soap) <- c("bacterial_counts", "method")

soap %>%
  count(method)
```

#### 1. Make an appropriate plot of the data.

```{r}
ggplot(data = soap, mapping = aes(x = bacterial_counts, color = method)) +
  geom_density()

ggplot(data = soap, mapping = aes(x = method, y = bacterial_counts)) +
  geom_boxplot()
```

#### 2. Conduct a test of the claim that all four methods are equally effective.

$H_0: \mu_1 = \mu_2 = \mu_3 = \mu_4$
$H_A:$ at least one of $\mu_1$, $\mu_2$, $\mu_3$, and $\mu_4$ is not equal to the others

```{r}
model_fit <- lm(bacterial_counts ~ method, data = soap)
summary(model_fit)
```

The p-value for the test is 0.001111.  There is very strong evidence against the null hypothesis that all four methods are equally effective.

#### 3. We will do this part on Monday: Conduct a test of the claim that the "Antibacterial Soap", "Soap", and "Water" methods are equally effective.

$H_0: \mu_2 = \mu_3 = \mu_4$
$H_A:$ at least one of $\mu_2$, $\mu_3$, and $\mu_4$ is not equal to the others

```{r}
soap <- soap %>%
  mutate(
    grouped_method = ifelse(method %in% c("Antibacterial Soap", "Soap", "Water"),
      "grouped", "Alcohol Spray")
  )

reduced_model_fit <- lm(bacterial_counts ~ grouped_method, data = soap)
anova(reduced_model_fit, model_fit)
```

The p-value for the test is 0.436.  The data do not offer any evidence against the null hypothesis that the "Antibacterial Soap", "Soap", and "Water" methods are equally effective.

#### 4. If you have extra time and want a refresher, calculate the mean and standard deviation of observations in each group

```{r}
soap %>%
  group_by(method) %>%
  summarize(
    mean_counts = mean(bacterial_counts),
    sd_counts = sd(bacterial_counts)
  )
```
